Test data

### 2022-07-17 Shiny/Test/Test data.Rmd
Fixes.

## Libraries
```{r}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny,tidyverse, scales, rvest, janitor, plotly, readxl, MetBrewer)
```

@@

# Testing with uniform currency
if (length(unique(kreft_html$valutakode)) == 1) {
  kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix =
                                    str_c(kreft_html$valutakode[1], " "))) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
} else {
    kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix = "? ")) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
}

>>>>

## Libraries
```{r libraries}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny,tidyverse, scales, rvest, janitor, plotly, readxl, MetBrewer)
```

@@

# Testing with uniform currency
if (length(unique(kreft_html$valutakode)) == 1) {
  kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix =
                                    str_c(kreft_html$valutakode[1], " "))) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation")
} else {
    kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = scales::label_dollar(prefix = "? ")) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
       subtitle = "Note: not all values are denominated in the same currency")
}
